Clustering time series based on probability distributions across temporal granularities

### 2021-11-10 main.Rmd
parcoord-application update

```{r opt-cluster-tsne-jsd, fig.cap = "(a) shows t-SNE summary of the $24$ selected customers chosen through prototype selection, (b) shows a plot of sindex for different cluster size."}

@@

```{r parcoord, fig.cap="Each of the 24 customers is represented by a parallel coordinate plot (a) with three wpd-based groupings. The plot shows that moy is the most important variable in identifying clusters, whereas wkdn-wday is the least significant and has the least fluctuation. One particular customer with high wpd across wknwday stands out in this display. Group 3 has a higher wpd for hod than moy or wkndwday. Group 2 has most discernible pattern across moy. Group 1 is a mixed group with strong patterns on atleast one of the three variables. All of these could be observed from the plot or the table (b) which shows median wpd values for each group.", message=FALSE, warning=FALSE}
include_graphics("figs/parcoord-application.png")
```

>>>>

```{r opt-cluster-tsne-jsd, fig.cap = "(a) shows t-SNE summary of the $24$ selected customers chosen through prototype selection, (b) shows a plot of sindex for different cluster size for clustering based on JS-based distances. The separation index decreases sharply from $5$ to $6$ clusters, so $5$ clusters are used here."}

@@

```{r parcoord, fig.cap="Each of the $24$ customers is represented by a parallel coordinate plot (a) with three wpd-based groupings. Plot (b) which shows median wpd values for each group. The plot shows that `moy` is the most important variable in identifying clusters, whereas `wnwd` is the least significant and has the least fluctuation. Two customers (id: 16 and 18) with high wpd across `wnwd` stand out in this display. Group 3 has a higher wpd for hod than moy or wkndwday. Group 2 has most discernible pattern across moy. Group 1 is a mixed group with strong patterns on atleast one of the three variables. All of these could be observed from the plot or the table (b).", message=FALSE, warning=FALSE}
include_graphics("figs/parcoord-application.png")
```
